%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

  %---------------------------------------------------------
  \cventry
  {Software Development Engineer I} % Job title
  {Amazon} % Organization
  {Seattle, Washington} % Location
  {Aug. 2021 - Current} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Designed and implemented a back-end service that utilized distributed programming to process large customer datasets into usable input data for Machine Learning models using Apache Spark and Python.}
      \item {Implemented a scheduling service to maintain and incrementally update customer data for our teams Machine Learning models using Java.}
      \item {Worked with team members and project managers to launch a new Alexa service to customers which resulted in automatic lighting control for over 1M Alexa customers.}
      \item {Setup and deployed AWS CloudWatch metrics and alarms for multiple services owned by my team using TypeScript and AWS CloudFormation.}
      \item {Helped launch a new feature/service that reduces friction in Alexa VUI for customers by predicting which device the customer is referring to and automatically performing actions.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Software Development Engineer Intern} % Job title
  {Amazon} % Organization
  {Seattle, Washington} % Location
  {Jun. 2020 - Sept. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Led the design and development of a back-end service which aggregates and encodes customer device data into machine learning embeddings for smart home devices.}
      \item {Created a design document for the new service using Amazon internal design document tools, technical writing skills, and UML diagrams.}
      \item {Deployed fully automated CI/CD pipelines using Amazon internal tools.}
      \item {Built and deployed overall service infrastructure utilizing several AWS services(Including CloudFormation, Lambda, DynamoDB, CloudWatch, IAM), focusing on high-availability, fault tolerance, and auto-scaling.}
      \item {Learned and developed skills in reviewing and writing better code-reviews.}
      \item {Learned how to use unit testing frameworks like Junit to write proper unit tests for production code.}
    \end{cvitems}
  }

  %---------------------------------------------------------
  \cventry
  {Teacher Assistent for Computer Science} % Job title
  {University of Washington} % Organization
  {Bothell, Washington} % Location
  {Jan. 2020 - Mar. 2020} % Date(s)
  {
    \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Assisted professor in grading all of the tests, quizzes, and homework assignments for a classroom of 40+ students.}
      \item {Provided detailed feedback on each homework assignment to help students learn and improve.}
      \item {Helped guide students in the right direction whenever they had questions on homework or computer science concepts.}
    \end{cvitems}
  }

  %---------------------------------------------------------
\end{cventries}
